\Huge Conferences in an Era of Expensive Carbon

### 2019-06-20 main.tex
Little things

SIGPLAN has also been exploring how to mitigate a conference's CO2e emissions
by purchasing \emph{carbon
  offsets}~\cite{CarbonOFfsetReport}.
%
A carbon offset is sold by a vendor who uses the raised funds to finance an
activity that permanently avoids emitting some amount of greenhouse gases.
The veracity and permanence of this CO2e emission avoidance is certified by
a watchdog organization. (Typically, planting trees is not a certifiable
activity, since it's hard to guarantee the trees won't be cut down, but
installing methane capture devices on landfill sites or buying
fuel-efficient stoves to replace open-fire cooking in poor communities can
be.)
%
Many organizations, including companies such as Google, Dell, Microsoft,
General Motors, Delta Airlines, Lyft, and Expedia, numerous universities,
and some academic societies, now buy carbon offsets in order to reduce their
net footprint. ACM conferences can do the same, and the purchases can be
included in the public accounting we are proposing.  In fact, ACM recently
decided that conferences could offer attendees the option to pay for an offset during
registration; the conference then uses the designated funds to purchase the
offset from a qualified vendor.  Some conferences are also experimenting
with corporate sponsorship of bulk offsets for the whole conference.\footnote{It
should be noted that carbon offsets are a controversial tool.  Besides
issues with verifiability and permanence, some observers worry
that---especially given their currently artificially-low cost---they will encourage
complacency, leading organizations to postpone making the difficult changes
that will be required to sustainably decarbonize society.  We believe that
offsets are a short-term measure, to be considered in parallel with,
not instead of, more difficult cutting.}

@@

Ideally, at some point, governments will impose carbon pricing uniformly,
and all CO2e-intensive activities will have to pay it. But ACM can send a
strong message about the importance of this issue by acting now. In
particular, as several companies have shown, even an artificial ``internal
price'' on carbon creates a significant price signal that shapes behavior.
%
Thus, our second (more ambitious) proposal is: ACM should impose a a
surcharge on conferences based on their carbon footprint.  The charge should
be low at the beginning and increase steadily (and predictably) year on
year.
%
Conference organizers can then choose (on the basis of careful analysis of
data and weighing of benefits) how best to balance their budgets---whether
by decreasing emissions, increasing registration fees, soliciting additional
corporate sponsorship, or some combination. \mwh{Problem: We showed
  just above that it's hard to figure out what to do. Come back to
  this point here and say that the surcharge will spur bold choices?
  Maybe say that these choices won't necessarily be bad, but could be
  really great?}

@@

\bcp{I wish we could put a paragraph here about the long-term picture and
  the need to rethink scientific exchange and ACM's business model.  That
  will please our grumpy reviewer, and I think it's actually a point worth
  making.}

>>>>

SIGPLAN has also been exploring how to mitigate a conference's CO2e emissions
by purchasing \emph{carbon
  offsets}~\cite{CarbonOFfsetReport}.
%
A carbon offset is sold by a vendor who uses the raised funds to finance an
activity that permanently avoids emitting some amount of greenhouse gases.
The veracity and permanence of this CO2e emission avoidance is certified by
a watchdog organization. (Typically, planting trees is not a certifiable
activity, since it's hard to guarantee the trees won't be cut down, but
installing methane capture devices on landfill sites or buying
fuel-efficient stoves to replace open-fire cooking in poor communities can
be.)
%
Many organizations, including companies such as Google, Dell, Microsoft,
General Motors, Delta Airlines, Lyft, and Expedia, numerous universities,
and some academic societies, now buy carbon offsets in order to reduce their
net footprint. ACM conferences can do the same, and the purchases can be
included in the public accounting we are proposing.  In fact, ACM recently
decided that conferences could offer attendees the option to pay for an
offset during registration; the conference then uses the designated funds to
purchase the offset from a qualified vendor.  Some conferences are also
experimenting with corporate sponsorship of bulk offsets for the whole
conference.\footnote{We acknowledge that carbon offsets are a
  controversial tool\bcp{Cite the thing the reviewer pointed us to, as well
    as the recent controversial UN report.}.  Besides issues with
  verifiability and permanence, some observers worry that---especially given
  their currently artificially-low cost---they will encourage complacency,
  leading organizations to postpone making the difficult changes that will
  be required to sustainably decarbonize society.  We believe that offsets
  are a short-term measure, to be considered in parallel with, not instead
  of, more difficult cutting.}

@@

Ideally, at some point, governments will impose carbon pricing uniformly,
and all CO2e-intensive activities will have to pay it. But ACM can send a
strong message about the importance of this issue by acting now. In
particular, as several companies have shown, even an artificial ``internal
price'' on carbon creates a significant price signal that shapes behavior.
%
Thus, our second (more ambitious) proposal is: ACM should impose a a
surcharge on conferences based on their carbon footprint.  The charge should
be low at the beginning and increase steadily (and predictably) year on
year.
%
Conference organizers can then choose (on the basis of careful analysis of
data and weighing of benefits) how best to balance their budgets---whether
by decreasing emissions, increasing registration fees, soliciting additional
corporate sponsorship, or by other, more creative, means. \mwh{Problem: We showed
  just above that it's hard to figure out what to do. Come back to
  this point here and say that the surcharge will spur bold choices?
  Maybe say that these choices won't necessarily be bad, but could be
  really great?}

@@

\bcp{I wish we could put a paragraph here about the long-term picture and
  the need to rethink scientific exchange and ACM's business model.  That
  will please our grumpy reviewer, and I think it's actually a point worth
  making.\cite{NCN}}
